\documentclass[11pt]{article}
\usepackage[margin=0.72in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{xcolor}
\usepackage{enumitem}
\pagestyle{empty}
\definecolor{gold}{HTML}{B98518}
\definecolor{ink}{HTML}{17130A}
\setlength{\parindent}{0pt}
\setlist[itemize]{leftmargin=14pt,itemsep=4pt,topsep=5pt}

\begin{document}

{\Huge \bfseries Goldmine Starter}\\[4pt]
{\large A free one-page map for viral social money ideas}\\[10pt]
\textcolor{gold}{\rule{\linewidth}{1.2pt}}

\vspace{10pt}
\textbf{What this is:} a quick taste of the full Goldmine PDF. The full version will personalize ideas based on your skills, interests, time, budget, platform preference, and comfort on camera.

\vspace{10pt}
\textbf{Three starter plays to think about}
\begin{itemize}
  \item \textbf{Faceless AI shorts:} pick one niche question, turn it into a 30-second explainer, and repeat the format daily.
  \item \textbf{AI influencer affiliate page:} create a niche character or editorial page, then route attention into product links and an email list.
  \item \textbf{UGC ad concept factory:} make hooks, scripts, and rough AI-generated ad concepts that small brands can test.
\end{itemize}

\vspace{6pt}
\textbf{Best first niche filter}

Choose something with: frequent trends, obvious products/tools to recommend, and content people already share. Good examples: AI tools for students, creator gear, fitness shortcuts, travel hacks, finance explainers, or productivity workflows.

\vspace{10pt}
\textbf{Your first move this week}
\begin{enumerate}[leftmargin=16pt,itemsep=4pt,topsep=5pt]
  \item Pick one niche and one platform.
  \item Write 10 hooks before making anything.
  \item Ship three posts using the same repeatable format.
\end{enumerate}

\vfill
\textcolor{gold}{\rule{\linewidth}{0.8pt}}\\[6pt]
\textbf{Want the full pack?} The \$1 Goldmine PDF expands this into 15--25 ranked ideas, a niche map, channel starter pack, AI workflows, monetization paths, and a 7-day action plan.\\
\textit{No guaranteed-income claims. Use this as a practical starting map, not financial advice.}

\end{document}
